Printer ballistics through character's texture analysis

### 2013-11-17 Printer_Ballistics.tex
Printer Ballistics...

\begin{table}
\begin{center}
\begin{tabular}{l*{6}{c}r}
Team              & P & W & D & L & F  & A & Pts \\
\hline
Manchester United & 6 & 4 & 0 & 2 & 10 & 5 & 12  \\
Celtic            & 6 & 3 & 0 & 3 &  8 & 9 &  9  \\
Benfica           & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
FC Copenhagen     & 6 & 2 & 1 & 2 &  5 & 8 &  7  \\
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{l*{2}{c}r}
Printer           & Documents \\
\hline
Brother-HL4070CDW & 28 \\
Canon-D1150 & 28 \\
Canon-MF3240 & 28 \\
Canon-MF4370DN & 28 \\
HP-CLJ-CP2025A & 28 \\
HP-CLJ-CP2025B & 28 \\
HP-JL-CP1518 & 28 \\
Lexmark-E260D & 28 \\
OKI-C330 & 28 \\
Samsung-CLP315 & 28 \\
\end{tabular}
\end{center}
\end{table}
